Symmetric Peer-to-Peer Applications

### 2024-07-30 spe-24/spe.tex
- spe-24

\documentclass[sn-mathphys,iicol]{sn-jnl}% Math and Physical Sciences Reference Style 
%\documentclass[default,iicol]{sn-jnl}% Default with double column layout

\jyear{2022}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

@@

\abstract{
In real-time networked applications, such as shared documents, users can
interact remotely and yet share the exact same experience as if they were in a
single machine.
%
In this work, we propose a middleware for \emph{symmetric peer-to-peer
applications} in which decentralized instances can broadcast asynchronous
events and yet conform to identical behavior.
%
Peers are allowed to join and leave the network at any time.
Application developers must adhere to a restricted API, which is deterministic,
stateless, and only supports pre-allocated memory.
%
The middleware is responsible for synchronizing the events in a global shared
timeline across the network.
Also, based on memory snapshots and deterministic simulation, a ``time machine''
can rollback conflicting peers to resynchronize their state.
%
We show that the middleware can handle applications with over 20 peers in a
heterogeneous topology under high churn.
For instance, in a simulation scenario of 25 events per minute with a network
latency of $50ms$, the peers need to roll back and resynchronize only $3\%$ of
the time.
}

@@

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

@@

The middleware is written in C and relies on the library \emph{SDL}%
\footnote{SDL: \url{http://www.libsdl.org}}
to deal with the network, timers, and input events, such as mouse clicks and
key presses.
The full source code%
\footnote{TODO}
is under 500 lines of code.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{move}
    \caption[XXX] {
        A moving rectangle is controlled by peers connected indirectly.
        Users can press \code{↑ ↓ → ←} to change the direction of the
        rectangle or \code{SPACE} to pause the application.
        The inputs are applied simultaneously in all peers, as if they were
        mirrors of a single application.
        Video: \url{http://youtube.com/TODO}
        \label{fig.move}
    }
\end{figure}

@@

\bibliography{p2p-22}

>>>>

\documentclass[sn-mathphys,iicol]{sn-jnl}

\jyear{2024}

\raggedbottom

@@

\abstract{
In real-time networked applications, such as shared documents, users can
interact remotely and yet share the exact same experience as if they were in a
single machine.
%
In this work, we propose a middleware for \emph{symmetric peer-to-peer
applications} in which decentralized instances can broadcast asynchronous
events and yet conform to identical behavior.
%
Peers are allowed to join and leave the network at any time.
Application developers must adhere to a restricted API, which is deterministic,
stateless, and only supports pre-allocated memory.
%
The middleware is responsible for synchronizing the events in a global shared
timeline across the network.
Also, based on memory snapshots and deterministic simulation, a ``time machine''
can rollback conflicting peers to resynchronize their state.
%
We show that the middleware can handle applications with over 20 peers in a
heterogeneous topology under high churn.
For instance, in a simulation scenario of 25 events per minute with a network
latency of 50ms, the peers need to roll back and resynchronize only 3\% of
the time.
}

@@

@@

The middleware is written in C and relies on the library \emph{SDL}%
\footnote{SDL: \url{http://www.libsdl.org}}
to deal with the network, timers, and input events, such as mouse clicks and
key presses.
The full source code%
\footnote{https://github.com/fsantanna/p2p-tml}
is around 500 lines of code.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{move}
    \caption[XXX] {
        A moving rectangle is controlled by peers connected indirectly.
        Users can press \code{↑ ↓ → ←} to change the direction of the
        rectangle or \code{SPACE} to pause the application.
        The inputs are applied simultaneously in all peers, as if they were
        mirrors of a single application.
        Video: \url{https://youtu.be/zkl0vSOGino}
        \label{fig.move}
    }
\end{figure}

@@

\bibliography{spe}
